Models

### 2023-06-15 analysis/05_model_metrics.Rmd
small update

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
library(emmeans)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
#get data
load(here::here("data/meta.rda"))
load(here::here("data/bt_traitfiltered.rda"))
load(here::here("data/rarefied_metrics.rda"))

@@

# There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
# tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()
# 
# pmap_df(tofit_mods %>% select(metric_name = metric, filter_study_id = study_id), function(metric_name, filter_study_id) {model_data %>%
#          filter(metric_name == metric, study_id == filter_study_id) %>%
#         mutate(n = n(), nrarefyID = n_distinct(rarefyID)) %>%
#         select(metric, study_id, nrarefyID, n) %>%
#         distinct()}) %>% View()

@@

Write out table of model estimates for manuscript
```{r}
#manuscript table
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))

#supplement of complete model output
bind_rows(metric_model_table, indv_mod_table) %>%
    select(-c(model_id, n_ts, warning, lower.CL, upper.CL, significant, REML, bobyqa)) %>%
  write_csv(here::here("paper", "model_estimates_supp.csv"))

@@

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
indv_mod_table %>% 
  filter(term == "year_scaled", p.value < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  mutate(positive = ifelse(estimate > 0, TRUE, FALSE)) %>%
  group_by(metric, positive) %>% 
  summarise(n_study_id = n_distinct(study_id))

>>>>

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
library(emmeans)
library(purrr)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
#get data
load(here::here("data/meta.rda"))
load(here::here("data/bt_traitfiltered.rda"))
load(here::here("data/rarefied_metrics.rda"))

@@

# There are 12 study/metric combos that can't be fit due to data limitations (too many rarefyID's )
# tofit_mods <- bad_indv_results2 %>% filter(!is.na(warning)) %>% select(metric, study_id, formula) %>% distinct()
# 
# missing_indv_studies <- pmap_df(tofit_mods %>% select(metric_name = metric, filter_study_id = study_id), function(metric_name, filter_study_id) {model_data %>%
#          filter(metric_name == metric, study_id == filter_study_id) %>%
#         mutate(n = n(), nrarefyID = n_distinct(rarefyID)) %>%
#         select(metric, study_id, nrarefyID, n) %>%
#         distinct()})

@@

Write out table of model estimates for manuscript
```{r}
#manuscript table
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  readr::write_csv(here::here("figures", "man_model_table.csv"))

#supplement of complete model output
bind_rows(metric_model_table, indv_mod_table) %>%
    select(-c(model_id, n_ts, warning, lower.CL, upper.CL, significant, REML, bobyqa)) %>%
  readr::write_csv(here::here("paper", "model_estimates_supp.csv"))

@@

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
indv_mod_table %>% 
  filter(term == "year_scaled", p.value < 0.05) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  mutate(positive = ifelse(estimate > 0, TRUE, FALSE)) %>%
  group_by(metric, positive) %>% 
  summarise(n_study_id = n_distinct(study_id)) %>%
  pivot_wider(names_from = "metric", values_from = "n_study_id")
